### 2021-07-08 msgauge-multisym.tex
Section 3, first draft.

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usetikzlibrary{positioning}
\usepackage{multicol}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
	Consider now $\omega$ \alert{$n$-plectic}
	\vfill
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
	\end{center}
	\vfill
	\only<1-3>{
	\begin{itemize}
		\item<2-> Higher analogue of the Courant algebroid $\rightsquigarrow$ \alert{\emph{Vinogradov algebroid}}
			\begin{displaymath}
			E^n = \left(TM\oplus\bigwedge^{n-1}T^\ast M \right)
			\end{displaymath}
		\item<3->  Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
		\\ Associated $L_\infty$-algebra on the graded vector space
		\begin{displaymath}\label{eq:VSpace}
			{\mathcal{V}^k} =
			\begin{cases}
				\mathfrak{X}(M)\oplus \Omega^{n-1}(M)  &\quad k=0,\\
				\Omega^{n-1+k}(M) &\quad -n+1 \leq k < 0.
			\end{cases}
		\end{displaymath}
	\end{itemize}
	}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Compatibility with Gauge transformations}
	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
	\vfill
	%
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Gauge_Diagram_k-plectic}
	\end{center}	
	%
	\vfill
	%

>>>>

%- Packages ----------------------------------------------------------------------------------------------
\usepackage{custom-style}
\usetikzlibrary{positioning}
\usepackage{multicol}
\DeclareMathOperator{\varv}{\mathscr{v}}

@@

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Vinogradov Algebroids}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Vinogradov Algebroids}
	\begin{defblock}[Vinogradov algebroid (higher Courant)]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_vinogradov}	
	\end{defblock}

	\begin{itemize}
		\item $(n=1) ~ \Rightarrow$ standard twisted \emph{Lie algebroid};
		\item $(n=2) ~ \Rightarrow$ standard twisted \emph{Courant algebroid};
	\end{itemize}

\end{frame}
\note[itemize]{
\item Att, questa definizione sarebbe lo standard twisted. E' possibile trovare in letteratura definizioni piu' generali corrispondenti alla nozione di Courant algebroid in astratto.
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Vinogradov $L_\infty$-algebra}
	Vin. alg.oids are $NQ$-manifolds ($L_\infty$-algebroids).
	$\quad\Rightarrow\quad$ 
	Associated $L_\infty$-algebra.

	\begin{defblock}[Vinogradov $L_\infty$-algebra \cite{Zambon2012}]
		\includestandalone[width=0.95\textwidth]{Pictures/Figure_vinogradov-Linfty}	
	\end{defblock}
	\vfill
	\only<6->{
		\tikz[overlay,remember picture]
		{
			\node[rounded corners,
                 fill=gray!1,draw=gray!30,anchor=base]            
            	 (base) at ($(current page.south)+(0,.5)$) [rotate=-0,text width=10cm,align=center] { \footnotesize{\color{gray}{
            	 $e_i = \pair{X_i}{\alpha_i} \in \mathfrak{X}(M)\oplus \Omega^{n-1}(M)$ 
            	 \quad~,\qquad
            	 $f_i \in \bigoplus_{k=0}^{n-2}\Omega^k(M)$.
            	 }}};
		}			
	}

\end{frame}
\note[itemize]{
	\item The actions of non vanishing multi-brackets (up to permutations of the entries) on arbitrary vectors
are given in the slide.
	\item $\mu_2 \left(e_1,e_2\right) 	= [e_1,e_2]_\omega 
			= \pair{[X_1,X_2]}{\dd \langle e_1, e_2\rangle_- 
			+ (\iota_{X_1}\dd\alpha_2 - \iota_{X_2}\dd\alpha_1 + \iota_{X_1}\iota_{X_2}\omega)}$
	\item $				\mu_2 \left(e_1,f_2\right) = -\mu_2(f_2,e_1) = 
				\frac{1}{2} \mathcal{L}_{X_1} f_2 = \langle e_1, \dd f_2 \rangle_-$
	\item $k$-ary bracket for $k \ge 3$ an \emph{odd} integer:	 
		\begin{equation}\label{eq:VinoMultibrakAllaZambon_1}
			\begin{split}
				\mu_k(\varv_0,\cdots,\varv_{k-1})
				=&
				\left(\sum_{i=0}^{k-1} {(-)^{i-1}\mu_k(f_i+\alpha_i,X_0,\dots,\widehat{X_i},\dots,X_{k-1})}\right)
				+\\
				&+(-)^{\frac{k+1}{2}} \cdot k \cdot B_{k-1} \cdot 
				\iota_{X_{k-1}}	\dots \iota_{X_{0}} \omega			
				~;
			\end{split}
		\end{equation}
		where 
		\begin{equation}\label{eq:VinoMultibrakAllaZambon_2}
			\begin{split}
			\mu_k&(f_0+\alpha_0,X_1,\dots,X_{n-1}) =
			\\
			&=
			~c_k
			\sum_{1\le i<j\le k-1}(-1)^{i+j+1}\iota_{X_{k-1}}\dots   
  			\widehat{\iota_{X_{j}}}\dots \widehat{\iota_{X_{i}}}\dots
				\iota_{X_{1}} ~ [f_0+\alpha_0,X_i,X_j]_3~.
			\end{split}
		\end{equation}			
In the above formula,		$[\cdot,\cdot,\cdot]_3 = -T_0$ denotes the ternary bracket %$\mu_3$ 
associated to the untwisted ($\omega=0$) Vinogradov Algebroid, and $c_k$ is a numerical constant
		\begin{equation}\label{eq:UglyCoefficient}
			c_k= (-)^{\frac{k+1}{2}}\frac{12~B_{k-1}}{(k-1)(k-2)}.
		\end{equation}
}
%-------------------------------------------------------------------------------------------------------------------------------------------------

%-------------------------------------------------------------------------------------------------------------------------------------------------
\subsection{Rogers embedding}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}[fragile]{Embedding observables $L_\infty$-algebra into Vinogradov $L_\infty$-algebra}
	Consider now $\omega$ \alert{$n$-plectic}
	\vfill
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Embedding_Diagram_k-plectic_V1}
	\end{center}
	\vfill
	\only<1-3>{
		.
	}

@@

\subsection{Compatibility with Gauge transformations}
%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{frame}{Compatibility with Gauge transformations}
	Consider now $\omega$ \alert{n-plectic} \quad and \alert{$\tilde{\omega}=\omega + d B$}:
	\vfill
	%
	\begin{center}
		\includestandalone[width=.8\textwidth]{Pictures/Frame_Gauge_Diagram_k-plectic}
	\end{center}	
	%
	\vfill
	%
